---
title: "PRGAT201Targets_20230324_plate5"
author: "Liz Hughes"
date: "2023/04/04"
output: output:
  html_document:
    toc: yes
    toc_depth: 2
  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Plate Reader 5: 20230329
Test WT KN99-alpha and GAT201 deletion mutant 003(Madhani), CAS3 deletion mutant, CCP1 deletion mutant, ISP6 deletion mutant in RPMI at 37 degrees.
3 Bioreps, 3 Techreps each.
Also, testing the growth phenotype of 1 of the double GAT201 strains P2.7ZH, 1 BioRep, 3 TechReps each.
Grow 5ml culture from colony (1 colony = 1 Biorep) in YPD, 30C, 180 rpm ON.
Seed at OD 600nm = 0.2 , 200 ul per well.
Run for 2 days (296 cycles).

```{r load_packages_5}

library("reshape2")
library(dplyr)
library(ggplot2)
library(tidyverse)
library(rmarkdown)
library(cowplot)
library(yaml)
library(knitr)
```



# Read in transposed data as csv file RPMI

```{r csv_file_5}

rawdata <- read.csv("../Input/20230329_RPMI_Gat201Targets_Plate5_csv.csv")

```

# Change time in seconds to time in days RPMI

```{r mutate_time_5}

 rawdata_day<-mutate(rawdata, Time = Time/86400)

```

# Tidy the data using the melt function from reshape2 RPMI

```{r reshape_5}

reshaped <- melt(rawdata_day, id=c("Time", "Temp"), 
                              variable.name="Well",
                              value.name="OD595")

summary(reshaped)
```

# Read in the Plate map data from csv file RPMI

```{r Load_platemap_5}

platemap <- read.csv("../Input/20230329_RPMI_Gat201Targets_Plate5_setup.csv")
head(platemap, n=50)


```

# Combine the reshaped data with the plate map, pairing them by Well 

```{r join_5}

annotated <- inner_join(reshaped, platemap, by="Well")
 
```

# How stable are ODs of blank wells, to use for normalisation? RPMI

```{r plot_blank_ODs_5}

ggplot(data=filter(annotated,Strain==""),
           aes(x=Time, y=OD595, color=Strain, group = Well)) + 
       geom_line() + 
       labs(x="Time (days)", y="Absorbance at 595 nm")
```


```{r plot_individual_blank_wells_5}

ggplot(data=filter(annotated,Well=="B12"), 
       aes(x=Time, y=OD595, color=Strain, group = Well)) + 
       geom_line() + 
     theme_bw()+
     labs(x="Time (hrs)", y="Absorbance at 595 nm")

```


Remove wells A2,A7,A12, H1, H3, H4, H5, H6, H9, H11, B1, D1, F1.

## Calculate median OD for blank wells for each growth medium RPMI


```{r calc_blank_medians_5}

blank_OD_summary <- annotated %>%
  filter(Strain=="") %>%
   filter(Well != "A2") %>%
  filter(Well != "A7") %>%
  filter(Well != "A12") %>%
  filter(Well != "H1") %>%
  filter(Well != "H3") %>%
  filter(Well != "H4") %>%
  filter(Well != "H5") %>%
  filter(Well != "H6") %>%
  filter(Well != "H9") %>%
  filter(Well != "H11") %>%
  filter(Well != "B1") %>%
  filter(Well != "D1") %>%
  filter(Well != "F1") %>%
  
    group_by(Media) %>%
  summarise(OD_median=median(OD595),
            OD_mean=mean(OD595),
            OD_max=max(OD595),
            OD_min=min(OD595))
print(blank_OD_summary)
```

# Subtract blank OD to make corrected OD and Plot OD_corrected v Time (hrs) RPMI

```{r subtract_blank_OD_5}

normalisedOD <- annotated %>%
  left_join(blank_OD_summary, by="Media") %>%
  mutate(OD_corrected = OD595 - OD_median)

```

## Plot OD all RPMI

```{r plot_all_5}

ggplot(data=normalisedOD %>%
                      filter(Strain != ""), 
                      aes(x=Time, y=OD_corrected, color=Strain, group = Well)) + 
       geom_line() + 
       scale_y_continuous(limits=c(0,0.075),expand=c(0,0))+
       facet_wrap(Strain ~ .)+
  
       labs(x = "Time(Hrs)",
            y = "Absorbance (595nm)") +
       theme(text = element_text(size = 20))+
       theme_bw()+
       scale_color_brewer(palette="Set1")
```
## Plot OD P2.7ZH (dbl GAT201) RPMI

```{r plot_P2.7ZH (dbl GAT201)}
ggplot(data=normalisedOD %>%
                      filter(Strain == "P2.7ZH (dbl GAT201)"), 
                      aes(x=Time, y=OD_corrected, color=Strain, group = Well)) + 
       geom_line() + 
       scale_y_continuous(limits=c(0,0.15),expand=c(0,0))+
       facet_wrap(Biorep ~ .)
  
       labs(x = "Time(Hrs)",
            y = "Absorbance (595nm)") +
       theme(text = element_text(size = 20))+
       theme_bw()+
       scale_color_brewer(palette="Set1")
```



## Plot OD all stat_summary(geom -"line") remove excess lines RPMI

```{r plot_stat_summary_5}

ggplot(data=normalisedOD  %>%
    dplyr::mutate(Strain = factor(Strain, levels = c("KN99 (WT)","GAT201","CAS3","CCP1","ISP6","CNAG_05458", "P2.7ZH (dbl GAT201)")))%>%
                     filter(Strain != ""), 
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
       #geom_line(aes(group = Well), size = 0.2, alpha = 0.2) + 
       stat_summary(fun = "median", geom = "line", size = 1) +
       scale_y_continuous(limits=c(0,0.1),expand=c(0,0), breaks = c(0, 0.05, 0.1)) +
  
       labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "GAT201 Targets", subtitle = "Plate 5: RPMI at 37 degrees") +
           
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 20))+
       theme(axis.title.y=element_blank()) +
       theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 20))+
       theme(panel.grid.minor = element_blank())+
       theme(legend.title = element_text(size = 15))+
      theme(legend.background = element_rect(fill = "transparent", color=NA))+
  theme(legend.key = element_rect(fill = "transparent", color=NA))+
       theme (plot.background =  element_rect(fill = "transparent", color=NA), 
         panel.background = element_rect(fill = "transparent", color=NA),)+
      theme(panel.border = element_rect(linetype = "solid", colour = "black", size = 2))+
   theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5) )+
       scale_color_brewer(palette="Set1")
       
```


```{r save_RMPI_PR5.png}

ggsave("../Results/AllSummaryPR5.png",width = 7,height=5)
```


## Plot OD all stat_summary(geom -"line") remove excess lines RPMI

```{r plot_stat_summary_minus P2,7ZH}

ggplot(data=normalisedOD  %>%
    dplyr::mutate(Strain = factor(Strain, levels = c("KN99 (WT)","GAT201","CAS3","CCP1","ISP6", "CNAG_05458")))%>%
                     filter(Strain != ""), 
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
        
       stat_summary(fun = "median", geom = "line", size = 1) +
       scale_y_continuous(limits=c(0,0.1),expand=c(0,0), breaks = c(0, 0.05, 0.1)) +
  
       labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "GAT201 Targets", subtitle = "Plate 5: RPMI at 37 degrees") +
           
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 20))+
       
       theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 20))+
       theme(panel.grid.minor = element_blank())+
       theme(legend.title = element_text(size = 15))+
      theme(legend.background = element_rect(fill = "transparent", color=NA))+
  theme(legend.key = element_rect(fill = "transparent", color=NA))+
       theme (plot.background =  element_rect(fill = "transparent", color=NA), 
         panel.background = element_rect(fill = "transparent", color=NA),)+
      theme(panel.border = element_rect(linetype = "solid", colour = "black", size = 2))+
   theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5) )+
       scale_color_brewer(palette="Set1")
       
```



```{r save_RMPI_PR5nodbldGAT201.png}

ggsave("../Results/AllSummaryPR5nodblGAT201.png",width = 6.6,height=5)
```


## Plot OD all stat_summary(geom -"line") Highlight summary line RPMI

```{r plot_all_stat_summary_5}

ggplot(data=normalisedOD %>%
    dplyr::mutate(Strain = factor(Strain, levels = c("KN99 (WT)","GAT201","CAS3","CCP1","ISP6","CNAG_05458", "P2.7ZH (dbl GAT201)")))%>%
                     filter(Strain != ""), 
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
       geom_line(aes(group = Well), size = 0.2, alpha = 0.2) + 
       stat_summary(fun = "median", geom = "line", size = 1) +
       scale_y_continuous(limits=c(0,0.1),expand=c(0,0), breaks = c(0, 0.05, 0.1)) +
   
       labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "GAT201 Targets", subtitle = "Plate 5: RPMI at 37 degrees") +
 
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 20)) +
  theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 20))+
    
       theme(legend.title = element_text(size = 15))+
  theme(panel.grid.minor = element_blank())+
   theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5) )+
  
       scale_color_brewer(palette="Set1")
```

```{r save_RMPI_PR5_GAT201.png}

ggsave("../Results/StatSummaryPlate5.png",width =7 ,height=5)
```

## Plot OD all stat_summary(geom -"line") remove excess lines RPMI for WT, GAT201 and dbl GAT201 P2.7ZH only

```{r plot_stat_summary_minus P2,7ZH}

ggplot(data=normalisedOD  %>%
    dplyr::mutate(Strain = factor(Strain, levels = c("KN99 (WT)","GAT201","P2.7ZH (dbl GAT201)")))%>%
                     filter(Strain != ""), 
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
        
       stat_summary(fun = "median", geom = "line", size = 1) +
       scale_y_continuous(limits=c(0,0.1),expand=c(0,0), breaks = c(0, 0.05, 0.1)) +
  
       labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "Double GAT201 Strain P2.7ZH", subtitle = "RPMI at 37 degrees") +
           
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 20))+
       
       theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 15))+
       theme(panel.grid.minor = element_blank())+
       theme(legend.title = element_text(size = 15))+
      theme(legend.background = element_rect(fill = "transparent", color=NA))+
  theme(legend.key = element_rect(fill = "transparent", color=NA))+
       theme (plot.background =  element_rect(fill = "transparent", color=NA), 
         panel.background = element_rect(fill = "transparent", color=NA),)+
      theme(panel.border = element_rect(linetype = "solid", colour = "black", size = 2))+
   theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5) )+
       scale_color_brewer(palette="Set1")
       
```

```{r save_RMPI_dblGAT201_P2.7ZH.png}

ggsave("../Results/StatSummaryP2_7ZH.png",width =7 ,height=5)
```

