---
title: "PRGAT201Targets_20230310_Plate3"
author: "Liz Hughes"
date: "2023/03/24"
output: 
  html_document:
    toc: yes
    toc_depth: 2
  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE , warning=FALSE, message=FALSE)
```


#Plate Reader 3: 20230310
Test WT KN99-alpha and GAT201 deletion mutant 003(Madhani), CNAG_04874 deletion mutant, HXT1 deletion mutant and FYC2 deletion mutant in RPMI at 37 degrees.
4 Bioreps, 3 Techreps each.
Grow 5ml culture from colony (1 colony = 1 Biorep) in YPD, 30C, 180 rpm ON.
Seed at OD 600nm = 0.2 , 200 ul per well.
Run for 2 days (300 cycles).



```{r load_packages_3}

library("reshape2")
library(dplyr)
library(ggplot2)
library(tidyverse)
library(rmarkdown)
library(cowplot)
library(yaml)
library(knitr)
```



# Read in transposed data as csv file RPMI

```{r csv_file_3}

rawdata <- read.csv("../Input/20230321_RPMI_Gat201Targets_Plate3_csv.csv")

```

# Change time in seconds to time in days RPMI

```{r mutate_time_3}

 rawdata_day<-mutate(rawdata, Time = Time/86400)

```

# Tidy the data using the melt function from reshape2 RPMI

```{r reshape_3}

reshaped <- melt(rawdata_day, id=c("Time", "Temp"), 
                              variable.name="Well",
                              value.name="OD595")

summary(reshaped)
```

# Read in the Plate map data from csv file RPMI

```{r Load_platemap_3}

platemap <- read.csv("../Input/20230321_RPMI_Gat201Targets_Plate3_setup.csv")%>%     
            dplyr::mutate(
                    Strain = factor(Strain, 
                    levels = c("KN99 (WT)", "GAT201", "CNAG_04874", "HXT1", "FCY2"),
                    labels = c("WT", "gat201∆", "CNAG_04874∆", "hxt1∆", "fcy2∆"))
  )
head(platemap, n=10)


```

# Combine the reshaped data with the plate map, pairing them by Well 

```{r join_3}

annotated <- inner_join(reshaped, platemap, by="Well")
 
```

# How stable are ODs of blank wells, to use for normalisation? RPMI

```{r plot_blank_ODs_3}

ggplot(data=filter(annotated, is.na(Strain)),
          aes(x=Time, y=OD595,  group = Well)) + 
          geom_line() + 
          labs(x="Time (days)", y="Absorbance at 595 nm")
```


```{r plot_individual_blank_wells_3}

ggplot(data=filter(annotated,Well=="B12"), 
       aes(x=Time, y=OD595, group = Well)) + 
       geom_line() + 
      theme_bw()+
      labs(x="Time (hrs)", y="Absorbance at 595 nm")

```

Remove well A11, B1, C1, D1, F1, H2-H12

## Calculate median OD for blank wells for each growth medium RPMI


```{r calc_blank_medians_3}

blank_OD_summary <- annotated %>%
      filter(is.na(Strain), Time < 1/24) %>%
      filter(Well != "A11") %>%
      filter(Well != "B1") %>%
      filter(Well != "C1") %>%
      filter(Well != "D1") %>%
      filter(Well != "F1") %>%
      filter(Well != "H2") %>%
      filter(Well != "H3") %>%
      filter(Well != "H4") %>%
      filter(Well != "H5") %>%
      filter(Well != "H6") %>%
      filter(Well != "H7") %>%
      filter(Well != "H8") %>%
      filter(Well != "H9") %>%
      filter(Well != "H10") %>%
      filter(Well != "H11") %>%
      filter(Well != "H12") %>%
  group_by(Media) %>%
  summarise(OD_median=median(OD595),
            OD_mean=mean(OD595),
            OD_max=max(OD595),
            OD_min=min(OD595))
print(blank_OD_summary)
```

# Subtract blank OD to make corrected OD and Plot OD_corrected v Time (hrs) RPMI

```{r subtract_blank_OD_3}

normalisedOD <- annotated %>%
  left_join(blank_OD_summary, by="Media") %>%
  mutate(OD_corrected = OD595 - OD_median)

```

## Plot OD all RPMI

```{r plot_all_3}

ggplot(data=normalisedOD %>%
                      filter( !is.na(Strain) ), 
                      aes(x=Time, y=OD_corrected, color=Strain, group = Well)) + 
       geom_line() + 
       scale_y_continuous(limits=c(0,0.18),expand=c(0,0))+
       facet_wrap(Strain ~ .)+
  
       labs(x = "Time(Hrs)",
            y = "Absorbance (595nm)") +
       theme(text = element_text(size = 20))+
       theme_bw()+
       scale_color_brewer(palette="Set1")
```
## Plot OD FCY2 RPMI

```{r plot_FCY2}

ggplot(data=normalisedOD %>%
                      filter(Strain == "fcy2∆"), 
                      aes(x=Time, y=OD_corrected, color=Strain, group = Well)) + 
       geom_line() + 
       scale_y_continuous(limits=c(0,0.15),expand=c(0,0))+
       facet_wrap(Biorep ~ .)+
  
       labs(x = "Time(Hrs)",
            y = "Absorbance (595nm)") +
       theme(text = element_text(size = 20))+
       theme_bw()+
       scale_color_brewer(palette="Set1")
```



## Plot OD all stat_summary(geom -"line") remove excess lines RPMI

```{r plot_stat_summary_3}

ggplot(data=normalisedOD %>%
         filter( !is.na(Strain) ), 
    #dplyr::mutate(Strain = factor(Strain, levels = c("KN99 (WT)","GAT201","CNAG_04874","HXT1","FCY2")))%>%
                     
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
       
       stat_summary(fun = "median", geom = "line", size = 1) +
       scale_y_continuous(limits=c(0,0.15),expand=c(0,0), breaks = c(0, 0.05, 0.15)) +
  
       labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "GAT201 Targets", subtitle = "Plate 3: RPMI at 37 degrees") +
           
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 15))+
       theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 15))+
       theme(panel.grid.minor = element_blank())+
       theme(legend.title = element_text(size = 15))+
      theme(legend.background = element_rect(fill = "transparent", color=NA))+
  theme(legend.key = element_rect(fill = "transparent", color=NA))+
       theme (plot.background =  element_rect(fill = "transparent", color=NA), 
         panel.background = element_rect(fill = "transparent", color=NA),)+
      theme(panel.border = element_rect(linetype = "solid", colour = "black", size = 2))+
   theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5) )+
       scale_color_brewer(palette="Set1")
       
```


```{r save_RMPI_PR3all.png}

ggsave("../Results/AllSummaryPR3.png",width = 6.6,height=5)
```


## Plot OD all stat_summary(geom -"line") Highlight summary line RPMI

```{r plot_all_stat_summary_3}

ggplot(data=normalisedOD %>%
    #dplyr::mutate(Strain = factor(Strain, levels = c("KN99 (WT)","GAT201","CNAG_04874","HXT1","FCY2")))%>%
                    filter( !is.na(Strain) ), 
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
       geom_line(aes(group = Well), size = 0.2, alpha = 0.2) + 
       stat_summary(fun = "median", geom = "line", size = 1) +
       scale_y_continuous(limits=c(0,0.18),expand=c(0,0), breaks = c(0, 0.05, 0.18)) +
   
       labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "GAT201 Targets", subtitle = "Plate 3: RPMI at 37 degrees") +
 
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 15)) +
  theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 15))+
    
       theme(legend.title = element_text(size = 15))+
  theme(panel.grid.minor = element_blank())+
   theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5) )+
  
       scale_color_brewer(palette="Set1")
```

```{r save_RMPI_PR3summ.png}

ggsave("../Results/StatSummaryPlate3.png",width = 6.6,height=5)
```




